---
title: "WeTrainOnTestData: Titanic Survivers Classification"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

try(setwd("C:/Users/Moritz/OneDrive/GitHub/Trende_jazzmoe/kaggle-challenges/titanic-survivers"), silent = TRUE)
# include pummy dir

source("00-script.R")
```

## Things to check

* Many age variables are missing which might cause bias | run regression on age and estimate ages of missing values
* make a dummy for cabin no cabin | classify different cabin categories
* 

## Data Documentation

| Variable | Definition                                 | Key                                            |
|----------|--------------------------------------------|------------------------------------------------|
| survival | Survival                                   | 0 = No, 1 = Yes                                |
| pclass   | Ticket class                               | 1 = 1st, 2 = 2nd, 3 = 3rd                      |
| sex      | Sex                                        |                                                |
| Age      | Age in years                               |                                                |
| sibsp    | # of siblings / spouses aboard the Titanic |                                                |
| parch    | # of parents / children aboard the Titanic |                                                |
| ticket   | Ticket number                              |                                                |
| fare     | Passenger fare                             |                                                |
| cabin    | Cabin number                               |                                                |
| embarked | Port of Embarkation                        | C = Cherbourg, Q = Queenstown, S = Southampton |

## Exploratory Data Analysis

Analyze here relationships of variables. z.B Plot of fare and pclass

```{r}
glimpse(Train)
p5
p6
```
### Missing Data
```{r}
naFrame %>% kable
```


### Embarked

```{r}
emb.surv
emb.surv.chisq
```

Peoplo who embarked in Southhampton have significantly higher likelihood of dying.

### Age

## Training Models

### Random forrest with 10-fold cv
Best model so far Mod3 with accuracy of 0.83.
